\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-26 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

\medskip
Figures~\ref{fem_cv_represent_a}(a) and (b) show the continuous displacement of fluid 2 due to the injection of fluid 1. They also show the wetting phase 'fingering' through the four subdomains, demonstrating the preferential flow through high-permeability regions. Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}. The idea was to to study the effects of heterogeneity of a quadrant model geometry using the current element type. This, in large scale, is a problem that can be found in petroleum production operations.

>>>>

\medskip
Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1. They also show the wetting phase 'fingering' through the four subdomains, demonstrating the preferential flow through high-permeability regions. Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}. The idea was to to study the effects of heterogeneity of a quadrant model geometry using the current element type. This, in large scale, is a problem that can be found in petroleum production operations. \red{(PLEASE REVISE THE PARAGRAPH ... AND YOU HAVEN'T ADDRESSED MY PREVIOUS COMMENTS ....)}
